Covering Your Basis: Model-Agnostic Inference of LIGO-Virgos Binary Black Hole Spin Distribution

### 2022-08-08 src/tex/ms.tex
got some data and figures put in now

@@

\subsection{Parameterized Perturbations} \label{sec:perturbation_model}
\subsection{Generic Mass Model} \label{sec:nonparametric_model}
\section{Results} \label{sec:results}
\subsection{Mass Spectrum Inference with GWTC-3} \label{sec:GWTC3_inferece}
\section{Conclusions}\label{sec:conclusion}
\section{Acknowledgements}\label{sec:acknowledments}
This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
This work benefited from access to the University of Oregon high performance computer, Talapas.  This material is based upon work supported 
in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility 
fully funded by the National Science Foundation.
\software{
\textsc{Astropy}~\citep{2018AJ....156..123A},
\textsc{NumPy}~\citep{harris2020array},
\textsc{Matplotlib}~\citep{Hunter:2007},
\textsc{bilby}~\citep{Ashton_2019},
\textsc{GWPopulation}~\citep{Talbot_2019}
}
\bibliography{references}{}
\bibliographystyle{aasjournal}

>>>>

\begin{figure*}[ht!]
    \script{spline_basis_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/spline_basis_plot.pdf}
        \caption{Plot showing proper (left) and improper (right) MSpline bases with 20 degrees of freedom and equal weights for each component. The 
            difference penalty as described in Section II hinges on the fact that basis coeficients that are close produce smoother or flatter 
            curves. This means one does not want to use an improper basis (i.e. right) with a difference penalty as the resulting curve is not flat 
            with each component having equal weights.}
        \label{fig:spline_basis}
    \end{centering}
\end{figure*}

@@

\subsection{Parameterized Perturbations} \label{sec:perturbation_model}
\subsection{Generic Mass Model} \label{sec:nonparametric_model}
\section{Results} \label{sec:results}

\begin{figure*}[ht!]
    \script{mass_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
        \caption{Plot showing the primary mass (left) and mass ratio (right) distributions inferred with the 
        \textsc{MSpline} model (black) with 40 knots for $m_1$, and 15 knots for $q$. We show the results for the \textsc{PowerlawPeak} (blue) and 
        \textsc{PowerlawSpline} (orange) models fromthe LVK's GWTC-3 population analyses. Solid lines show the median of the posterior while the shaded
        bands show the 90\% credible intervals.}
        \label{fig:mass_distribution}
    \end{centering}
\end{figure*}

\begin{figure*}[ht!]
    \script{component_spin_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/component_spin_distribution_plot.pdf}
        \caption{Plot showing the inferred component spin magnitude (top) and spin tilt (bottom) distributions inferred with the 9-knot \textsc{MSpline} models. 
        There are two independent \textsc{MSpline} (black) models for each primary/secondary spin magnitude and spin tilt. We compare by showing the results for the
        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
        \label{fig:component_spin_distribution}
    \end{centering}
\end{figure*}

\subsection{Mass Spectrum Inference with GWTC-3} \label{sec:GWTC3_inferece}
\section{Conclusions}\label{sec:conclusion}
\section{Acknowledgements}\label{sec:acknowledments}
This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
This work benefited from access to the University of Oregon high performance computer, Talapas.  This material is based upon work supported 
in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility 
fully funded by the National Science Foundation.
\software{
\textsc{Astropy}~\citep{2018AJ....156..123A},
\textsc{NumPy}~\citep{harris2020array},
\textsc{Matplotlib}~\citep{Hunter:2007},
\textsc{bilby}~\citep{Ashton_2019},
\textsc{GWPopulation}~\citep{Talbot_2019}
}
\bibliography{references}{}
\bibliographystyle{aasjournal}
